%%%%%%%%%%%%%%%%%
% This is an sample CV template created using altacv.cls
% (v1.3, 10 May 2020) written by LianTze Lim (liantze@gmail.com). Now compiles with pdfLaTeX, XeLaTeX and LuaLaTeX.
% This fork/modified version has been made by Nicolás Omar González Passerino (nicolas.passerino@gmail.com, 15 Oct 2020)
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you need to pass whatever options to xcolor
\PassOptionsToPackage{dvipsnames}{xcolor}

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

%% Fork: CV dark mode toggle enabler to use a inverted color palette.
%% Use the "darkmode" option if you want a color palette used to 
% \documentclass[10pt,a4paper,darkmode]{altacv}

\documentclass[10pt,a4paper,ragged2e,withhyper]{altacv}

%% AltaCV uses the fontawesome5 and academicons fonts
%% and packages.
%% See http://texdoc.net/pkg/fontawesome5 and http://texdoc.net/pkg/academicons for full list of symbols. You MUST compile with XeLaTeX or LuaLaTeX if you want to use academicons.

% Change the page layout if you need to
\geometry{left=1.2cm,right=1.2cm,top=1cm,bottom=1cm,columnsep=0.75cm}

% The paracol package lets you typeset columns of text in parallel
\usepackage{paracol}

% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Roboto Slab}
  \setsansfont{Lato}
  \renewcommand{\familydefault}{\sfdefault}
\else
  % If using pdflatex:
  \usepackage[rm]{roboto}
  \usepackage[defaultsans]{lato}
  % \usepackage{sourcesanspro}
  \renewcommand{\familydefault}{\sfdefault}
\fi

% Fork: Change the color codes to test your personal variant on any mode
\ifdarkmode%
  \definecolor{PrimaryColor}{HTML}{0F52D9}
  \definecolor{SecondaryColor}{HTML}{3F7FFF}
  \definecolor{ThirdColor}{HTML}{F3890B}
  \definecolor{BodyColor}{HTML}{ABABAB}
  \definecolor{EmphasisColor}{HTML}{ABA2A2}
  \definecolor{BackgroundColor}{HTML}{242424}
  \definecolor{AboutColor}{HTML}{ABABAB}
\else%
  \definecolor{PrimaryColor}{HTML}{001F5A}
  \definecolor{SecondaryColor}{HTML}{0039AC}
  \definecolor{ThirdColor}{HTML}{F3890B}
  \definecolor{BodyColor}{HTML}{666666}
  \definecolor{EmphasisColor}{HTML}{2E2E2E}
  \definecolor{BackgroundColor}{HTML}{E2E2E2}
  \definecolor{AboutColor}{HTML}{222222}
\fi%

\colorlet{name}{PrimaryColor}
\colorlet{tagline}{PrimaryColor}
\colorlet{about}{AboutColor}
\colorlet{heading}{PrimaryColor}
\colorlet{headingrule}{ThirdColor}
\colorlet{subheading}{SecondaryColor}
\colorlet{accent}{SecondaryColor}
\colorlet{emphasis}{EmphasisColor}
\colorlet{body}{BodyColor}
\colorlet{hyperlink}{PrimaryColor}
\pagecolor{BackgroundColor}

% Change some fonts, if necessary
\renewcommand{\namefont}{\Huge\rmfamily\bfseries}
\renewcommand{\personalinfofont}{\small\bfseries}
\renewcommand{\cvsectionfont}{\LARGE\rmfamily\bfseries}
\renewcommand{\cvsubsectionfont}{\large\bfseries}
\renewcommand{\quote}{\normalsize}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%% sample.bib contains your publications
%% \addbibresource{sample.bib}

% Multi language CV
% Change the language used in this file. 
% Use `\entrue` or `\svtrue` for English/Swedish
\entrue
% Put in separate file for build script
%\input{build_lang.tex}

\begin{document}
    \name{Martin Blom}
    \tagline{\en{CSE Student}\sv{CSE Student}}
    %% You can add multiple photos on the left or right
    %%\photoR{3cm}{john-doe}
    
    \personalinfo{
        \email{martinblom@live.se}\smallskip
        \phone{+46-737021018}
        \location{\en{Gothenburg, Sweden}\sv{Göteborg, Sverige}}\\
        \linkedin{Martin Blom}{martin-blom-b459a5231}
        \github{Marre-B}
        %\homepage{nicolasomar.me}
        %\medium{nicolasomar}
        %% You MUST add the academicons option to \documentclass, then compile with LuaLaTeX or XeLaTeX, if you want to use \orcid or other academicons commands.
        % \orcid{0000-0000-0000-0000}
        %% You can add your own arbtrary detail with
        %% \printinfo{symbol}{detail}[optional hyperlink prefix]
        % \printinfo{\faPaw}{Hey ho!}[https://example.com/]
        %% Or you can declare your own field with
        %% \NewInfoFiled{fieldname}{symbol}[optional hyperlink prefix] and use it:
        % \NewInfoField{gitlab}{\faGitlab}[https://gitlab.com/]
        % \gitlab{your_id}
    }
    
    \makecvheader
    %% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
    % \AtBeginEnvironment{itemize}{\small}
    
    %% Set the left/right column width ratio
    \columnratio{0.26}

    % Start a 2-column paracol. Both the left and right columns will automatically
    % break across pages if things get too long.
    \begin{paracol}{2}
        % ----- STRENGTHS -----
        \cvsection{\en{Strengths}\sv{Styrkor}}
	\sv{
            \cvtag{Problemlösning} \\
            \cvtag{Stresstålig} \\
            \cvtag{Självsäker} \\
            \cvtag{Ansvarstagande} \\
            \cvtag{Noggrann} \\
	}
	\en{
	\cvtag{Problem solving} \\
            \cvtag{Stress resistant} \\
            \cvtag{Confidence} \\
            \cvtag{Responsible} \\
            \cvtag{Meticulous} \\
	 \cvtag{Quick Learner} \\
	}

            \medskip
            
        % ----- STRENGTHS -----
        
        % ----- CODING -----
        \cvsection{\en{Coding}\sv{Programspråk}}
	\sv{
            \cvtag{Haskell: Grundläggande} \\
	 \cvtag{Python: Grundläggande} \\
            \cvtag{Java: Grundläggande} \\
            \cvtag{C: Grundläggande} \\
	 \cvtag{C++: Grundläggande} \\
	 \cvtag{C\#: Grundläggande}
	}
	\en{
	 \cvtag{Haskell: Basic} \\
	 \cvtag{Python: Intermediate} \\
            \cvtag{Java: Basic} \\
	 \cvtag{Java/Type -Script: Basic} \\
            \cvtag{C: Basic} \\
	 \cvtag{C++: Intermediate} \\
	 \cvtag{C\#: Intermediate}
	}

            \medskip
            
        % ----- CODING -----
        
        % ----- LANGUAGES -----
        \cvsection{\en{Languages}\sv{Språk}}
            \cvlang{\en{Swedish}\sv{Svenska}}{\en{Native}\sv{Modersmål}}\\
            \medskip
            
            \cvlang{\en{English}\sv{Engelska}}{\en{Proficient / Fluent}\sv{Flytande}}
		\medskip
            
            \cvlang{\en{Croatian}\sv{Kroatiska}}{\en{Basic knowledge}\sv{Grundläggande kunskaper}}
            %% Yeah I didn't spend too much time making all the
            %% spacing consistent... sorry. Use \smallskip, \medskip,
            %% \bigskip, \vpsace etc to make ajustments.
            \smallskip
        % ----- LANGUAGES -----
        
        % ----- KÖRKORT -----
        \sv{\cvsection{Körkort}}\en{\cvsection{Licenses}}
         \cvevent{\en{Driver License}\sv{Körkort}}{}{\sv{Oktober 2019}\en{October 2019}}{}

                \begin{itemize}
                    \item B + AM 
                \end{itemize}

 	    \divider
            
         \cvevent{\en{Forklift License}\sv{Truckkort}}{| TLP10}{\sv{Februari 2022}\en{February 2022}}{}

                \begin{itemize}
                    \item A1, A2, A3, A4, B1, B2, B3, B4
                \end{itemize}

        % ----- KÖRKORT -----

        % ----- REFERENCES -----
        \cvsection{\en{References}\sv{Referenser}}
            \sv{%Andrea Leupold \\ Kundservice Chef \\ Volvo Car Retail \\
			%\email{andrea.leupold@volvocarretail.se}
			%\phone{08-580 00 633}
		Referens kan lämnas på efterfrågan.
	}
	\en{
		References can be sent on request.
	}
            \smallskip
        % ----- REFERENCES -----
        
        % \cvsection{A Day of My Life}

	% ---  \cvachievement{\faTrophy}{Fantastic Achievement}{and some details about it}\\
        
        % Adapted from @Jake's answer from http://tex.stackexchange.com/a/82729/226
        % \wheelchart{outer radius}{inner radius}{
        % comma-separated list of value/text width/color/detail}
        % \wheelchart{1.5cm}{0.5cm}{%
        %   6/8em/accent!30/{Sleep,\\beautiful sleep},
        %   3/8em/accent!40/Hopeful novelist by night,
        %   8/8em/accent!60/Daytime job,
        %   2/10em/accent/Sports and relaxation,
        %   5/6em/accent!20/Spending time with family
        % }
        
        % use ONLY \newpage if you want to force a page break for
        % ONLY the current column
        \newpage
        
        %% Switch to the right column. This will now automatically move to the second
        %% page if the content is too long.
        \switchcolumn
        
        % ----- ABOUT ME -----
        \cvsection{\en{About Me}\sv{Om mig}}
            \begin{quote}
                \en{
                    I'm a very happy, outgoing and generally knowledgeable person. I have a big interest in computers, programming and other tech, I'm also interested in hunting and like physical
		challenges as well as being out in nature. At the moment I'm studying my fifth consecutive year at Chalmers University of Technology, and currently on my second year of my masters
		 in High Performance Computer Systems.
                }
                \sv{
                    Jag är en väldigt glad, utåtgående och allmänt kunnig person. Jag har ett stort intresse i datorer, programmering och övrig teknik,
			 jag är också intresserad av jakt och gillar fysiska utmaningar/röra på mig och vara i naturen. Jag pluggar för tillfället mitt fjärde år på Chalmers
			 Tekniska Högskola där jag går mitt första år på masterprogrammet inom högpresterande datorsystem.
                }
            \end{quote}
        % ----- ABOUT ME -----
        
        % ----- EXPERIENCE -----
        \cvsection{\en{Experience}\sv{Erfarenhet}}
            \cvevent{\en{Production Manager}\sv{Produktionschef}}{| \en{McDonald's}\sv{McDonald's}}
			{\sv{September 2018 -- Augusti 2020}\en{September 2018 -- August 2020}}{\en{Katrineholm, Sweden}\sv{Katrineholm, Sverige}}
            \en{
               	 Worked mainly as production manager in the kitchen.
            }
            \sv{
                	På McDonald’s så jobbade jag till störst del i köket och gjorde då allt som tillkom, så som att se till att det fanns upptinade ingredienser, att alla maskiner var rena och fungerande och
		 tillaga maten. Jag är också utbildad inom alla serviceområden och stod ibland i kassan, plockade ihop beställningar och tog hand om drive-through’en. Jag har avklarad utbildning
		 som produktionschef och för att utbilda andra nya medarbetare, och en påbörjad utbildning för att jobba som skiftledare. \\
            }

		\divider

		\cvevent{\en{Customer Service Agent}\sv{Kundserviceagent}}{| \en{Volvo Car Retail (Consultant - Manpower)}\sv{Volvo Car Retail (Konsult - Manpower)}}
			{\sv{Maj 2022 -- September 2022}\en{May 2022 -- September 2022}}{\en{Gothenburg, Sweden}\sv{Göteborg, Sverige}}
             \en{
                	At Volvo I was responsible of smoothly and with great creativity handling every day issues. These issues  My tasks a a customer service agent involved a very broad work area with a lot of problem solving and customer service. A usual day 				could include things such as, ordering extra parts, making a workshop reservation, receiving and giving out rental cars as well as arranging test drives of both new and used cars. \\
            }
            \sv{
                	Här var jag anställd av Volvo Car Retail som konsult från Manpower. Jag jobbade på anläggningen Volvo Car Sörred i Torslanda området. I anläggningen hade vi både
		 återförsäljning av nya och gamla bilar, samt en verkstad och biluthyrning. Min arbetsuppgift som kundserviceagent involverade ett väldigt brett arbetsområde med mycket
		 problemlösning och kundbemötande. Jag stod i "receptionen" till anläggningen och är första personen man får kontakt med när man kommer in. Därifrån är det upp till mig att 
		se till att kunden får den hjälp de behöver, eller kommer till rätt person. En vanlig dag kunde involvera saker så som, att beställa reservdelar, att boka verkstadstid åt en kund,
		 att lämna ut/ta emot hyrbilar och arrangera provkörningar av både nya och begagnade bilar. \\
            }

	 \divider

		\cvevent{\en{Gothenburg Representative}\sv{Göteborg Representant}}{| \en{Wanda Sweden}\sv{Wanda Sweden}}
			{\sv{Oktober 2022 -- Maj 2024 }\en{October 2022 --  May 2024}}{\en{Gothenburg, Sweden}\sv{Göteborg, Sverige}}
            \en{
               	Wanda opened their first warehouse in Gothenburg in October of 2022 and I was the first on-site employee. From there on I had the main responsibility for our operations in 
		Gothenburg. My responsibilities aside from regular work was educating new employees and making sure everything around the warehouse and our servicces ketp working. 
		Since August of 2023 I have also had the responsibility of route planning/capacity management for all of the warehouses in Sweden. \\
            }
            \sv{
                	Wanda öppnade sitt första lager i Göteborg Oktober 2022 och jag belv den första annställda på plats. Jag har sedan dess haft mycket ansvar och varit huvudansvarig för vår
		 operation här i Göteborg då resterande av personalen -  inkluderat min närmsta chef -  i Sverige är belägna i Stockholm. Mitt ansvar utöver det vanliga arbetet har varit att lära upp
		 ny personal samt se till att allt kring lagret och våra tjänster fungerar och hålla min närmsta chef uppdaterad. Jag har sedan Augisti 2023 också varit ansvarig för rutt planering
		/kapacitet för alla våra lager i Sverige. \\
            }

	\divider

		\cvevent{\en{Software Developer}\sv{Göteborg Representant}}{| \en{Volvo Car}\sv{Wanda Sweden}}
			{\sv{Oktober 2022 -- Maj 2024 }\en{May 2024 --  August 2024}}{\en{Gothenburg, Sweden}\sv{Göteborg, Sverige}}
            \en{
               	 My work at Volvo Cars was as a summer intern supporting the Technical Leader (Contamination Team) in coding and processing data/models. During my time in this position 
		I wrote and developed a Python application for inhouse use as a database and data visualizer. The application was developed using mainly python libraries: SQLite and QTWidgets. \\
            }
            \sv{
                	a\\
            }
            
        % ----- EXPERIENCE -----
        
        % ----- EDUCATION -----
        \cvsection{\en{Education}\sv{Utbildning}}
            	\cvevent{\en{Technology Program}\sv{Teknikprogrammet}}{\sv{| Gymnasieskola}\en{| Upper secondary school}}
			{\sv{Augusti 2017 -- Juni 2020}\en{August 2017 -- June 2020}}{\en{Eskilstuna, Sweden}\sv{Eskilstuna, Sverige}}
            \en{
                Attended \link{Grillska Gymnasiet}{https://grillska.se/grillska-gymnasiet-eskilstuna}
                \smallskip
                \begin{itemize}
                    \item Grade Average: 19.98
                \end{itemize}
            }
            \sv{
                Gick på \link{Grillska Gymnasiet}{https://grillska.se/grillska-gymnasiet-eskilstuna}
                \smallskip
                \begin{itemize}
                    \item Betygssnitt: 19.98
                \end{itemize}
            }

            \divider
            
            	\cvevent{\en{Computer Science}\sv{Data- och informationsteknik}}{\sv{| Universitet}\en{| University}}
			{\sv{Augsti 2020 -- Juni 2025}\en{August 2020 -- June 2025}}{\en{Gothenburg, Sweden}\sv{Göteborg, Sverige}}
            \en{
 	      Attending \link{Chalmers University of Technology}{https://www.chalmers.se/en/Pages/default.aspx}
                \smallskip
                \begin{itemize}
                    \item GPA: N/A
                \end{itemize}
            }
            \sv{
	      Går på \link{Chalmers Tekniska Högskola}{https://www.chalmers.se/en/Pages/default.aspx}
	     \smallskip
                \begin{itemize}
                    \item Betygssnitt: N/A
                \end{itemize}
            }
	    \divider

        % ----- EDUCATION -----
        
        % ----- PROJECTS -----
\begin{comment}
        \cvsection{\en{Projects}\sv{Projekt}}
            \cvevent{\en{Project 1}\sv{Projekt 1}}{\cvrepo{| \faGithub}{https://github.com/user/repo}\cvrepo{| \faGlobe}{https://repo-demo.com/}}{Mm YYYY -- Mm YYYY}{}
            \en{
                \begin{itemize}
                    \item Item 1
                    \item Item 2
                \end{itemize}
            }
            \sv{
                \begin{itemize}
                    \item Punkt 1
                    \item Punkt 2
                \end{itemize}
            }
            \divider
            
            \cvevent{\en{Project 2}\sv{Projekt 2}}{\cvrepo{| \faGitlab}{https://gitlab.com/user/repo}\cvrepo{| \faGlobe}{https://repo-demo.com/}}{Mm YYYY -- Mm YYYY}{}
            \en{
                \begin{itemize}
                    \item Item 1
                    \item Item 2
                \end{itemize}
            }
            \sv{
                \begin{itemize}
                    \item Punkt 1
                    \item Punkt 2
                \end{itemize}
            }
\end{comment}
            
        % ----- PROJECTS -----
    \end{paracol}
\end{document}
